The complex structure and peculiar internal motions of the planetary nebula NGC 6210

### 2020-05-22 ms.tex
Add Beto figure captions.  These need some editing
In particular, the description of the HST images is not quite right.
The bottom panels are RGB combinations of various filters from some
press releases.  I should redo the combinations.

 \begin{figure}
\centering
  \includegraphics[width=0.4\textwidth]{tere-figs/Figure2a}
  \caption{ }
  \label{fig:slit-positions}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=1\textwidth]{tere-figs/Figure3}
  \caption{}
  \label{fig:pv-array}
\end{figure*}

@@

\begin{figure}
\centering
%\includegraphics[width=0.7\textwidth]{tere-figs/Figure8}
%\includegraphics[width=0.327\textwidth]{tere-figs/opo9836f}
%\includegraphics[width=0.32\textwidth]{tere-figs/N6210_ruso}
\includegraphics[width=\linewidth]{sketch}
\caption{}
\label{fig:hst}
\end{figure}

@@

\newpage
\section{Proper motions}
\label{sec:proper-motions}

>>>>

 \begin{figure}
\centering
  \includegraphics[width=0.4\textwidth]{tere-figs/Figure2a}
  \caption{Top panel shows the slit positions from the 2015 run, these are indicated as solid lines and 
labeled at the top against an [O III] HST image. Dashed lines refer to additional slit positions from other runs
and are labeled at the bottom of the image. The middle and bottom panels show the slit positions from 
the other runs placed at different position angles. }
  \label{fig:slit-positions}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=1\textwidth]{tere-figs/Figure3}
  \caption{Position--velocity line profiles for the slit positions from the 2015 run are shown in sets where
the H$\alpha$ bi-dimensional line profile is on the left panel of the set, the \oiii{} line profile is on the central panel 
and the \nii{} line profile is on the right panel. The corresponding slit positions are indicated at the top of
each set of line profiles. The velocity scale is heliocentric and the spatial scale is indicated in arcsec 
with respect to the center of the nebula.}
  \label{fig:pv-array}
\end{figure*}

@@

\begin{figure}
\centering
%\includegraphics[width=0.7\textwidth]{tere-figs/Figure8}
%\includegraphics[width=0.327\textwidth]{tere-figs/opo9836f}
%\includegraphics[width=0.32\textwidth]{tere-figs/N6210_ruso}
\includegraphics[width=\linewidth]{sketch}
\caption{mages from the HST archive are shown on the bottom panels,  \oiii{} (left) and \nii{} (right), and their
corresponding images are shown in the top panels processed with a natural logarithm function and an edge 
detection algorithm. The most salient features in these images are indicated and labeled for reference.}
\label{fig:hst}
\end{figure}

@@

\section{Proper motions}
\label{sec:proper-motions}
